# Ethics

Do no harm!

In research ethics and governance there is a lot of discussion about informed consent, not disclosing personal information and so on.

Sometimes these come up when fitting models to criminological data- UKDS requires that any results you produce don't refer to an unweighted base population of less than 50.

Strictly speaking, this means that if you fit a logistic regression model with a categorical independent variable you need to have more than 50 people in each response category.

This can

```{r}

library(tidyverse)

set.seed(1234)

n_size <- 5568

# approximate sample size for Scottish Crime and Justice Survey

# The 2011 census found that:
# Scotland's population was 96.0% white

# https://www.scotlandscensus.gov.uk/census-results/at-a-glance/ethnicity/

dat <- tibble(
  ethnicity = sample(c("white scottish/british/other", "minority ethnic"),
       size = n_size,
       prob = c(0.96, 0.04),
       replace = TRUE)
)

# simulate victimization data

dat <- 
dat |> 
  mutate(minority_ethnic = if_else(ethnicity == "minority ethnic", 1, 0),
         vict =
                    rbinom(n = n_size, 
                       size = 1, # either 1 or 0,
                       prob = plogis(-2 +  minority_ethnic * 0.5)))

dat |> 
  count(ethnicity, vict) |> 
  group_by(ethnicity) |> 
  mutate(prop = n / sum(n))


plogis(-2) # 11%

plogis(-2 + 0.5) # 18% - I just made this up, I don't know if this is accurate!

# if you publish the marginal breakdown by ethnicity in table one

dat |> 
  count(ethnicity)

# and then the regression coefficients

glm(vict ~ ethnicity, family = "binomial", data = dat) |> 
  summary()
```

```{r}


# a reader could calculate the probability of victimization using the inverse
# link function and then multiply this by the number of minority ethnic people
# to recover the sample size

plogis(-1.4253) * 227
         
```

This may not apply in every case, but it is worth checking, particularly if you wanted to include things like interaction terms between categorical variables in a logistic regression model.

## Reproducible research practices?

Make sure the data is right!!

https://github.com/jkangbrown/when_police_replication

## Framing

More conceptually, it's important to think about how we frame the results of any analysis.

Three visualizations from [Data Feminism](https://data-feminism.mitpress.mit.edu/pub/czq9dfs5/release/3) 

-   language use

-   providing necessary context?

-   deficit narrative

-   the description of your charts is theoretically informed

### community loss

Jessica Simes [@simesPunishingPlacesGeography2021] gives a good example of how we may want to come up with theoretically informed measures, or theoretically re-frame measures. Simes analysed imprisonment data from the state of Massachusets in the USA, including spatial regression of prison admission rates and how these relate to "racial demographics, social and economic disadvantage, arrest rates, and violent crime" [@simesPlacePunishmentSpatial2018a].

As part of this analysis Simes suggests that the cumulative years sentenced to residents of a particular neighbourhood be thought of as 'community loss'. This is not (just?) an indicator of individual punishment histories, but reflects the chronic and long-term exposure to loss due to imprisonment in different neighbourhoods. This highlights the effects of imprisonment on the communities in which people who end up in prison lived prior to their imprisonment, rather than just focusing on the people who are currently in prison.
